Brownian Dynein Model

### 2015-10-11 latex/derivation.tex
New cartesian solving strategy: simplify up to Ln/Lf in Latex, solve for actual angles in C.

@@

We then expand $L_{n}$...

\begin{align}
  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\Big)\Big(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\Big) \mp \\
  & \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\bigg)^2}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\bigg)^2} \pm \\
  & \frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2+-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
\end{align}

@@

\begin{align}
  X_{t} &= L_n\cos(\Theta_{1}) \\
       &= \frac{L^2+L_n^2-L_f^2}{2L} \\
       &= \frac{L^2 + L_s^2 + L_t^2 - 2L_tL_s\cos(\Theta_{nm}) - L_s^2 - L_t^2 + 2L_sL_t\cos(\Theta_{fm})}{2L} \\
       &= \frac{L^2 + 2L_tL_s\big(\cos(\Theta_{fm})-\cos(\Theta_{nm})\big)}{2L}
\end{align}

@@

\begin{align}
  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
  Y_{t} &= L_n\sin(\Theta_{1}) \\
       &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
       &= L_n\sqrt{1 - (\frac{L^2+L_n^2-L_f^2}{2LL_n})^2} \\
\end{align}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{nb} &= 0 \\
  X_{nm} &= L_{s}*\cos(\Theta_{nb}) \\
  X_{t}  &= ?? \\
  X_{fm} &= L_{s}*\cos(\Theta_{fb}) \\
  X_{fb} &= L \\
\end{align}

\begin{align}
  Y_{nb} &= 0 \\
  Y_{nm} &= L_{s}*\sin(\Theta_{nb}) \\
  Y_{t}  &= ?? \\
  Y_{fm} &= L_{s}*\sin(\Theta_{fb}) \\
  Y_{fb} &= 0
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= -L_{s}*\sin(\Theta_{nb})*\dot{\Theta}_{nb} \\
  \dot{X}_{t } &= ?? \\
  \dot{X}_{fm} &= -L_{s}*\sin(\Theta_{fb})*\dot{\Theta}_{fb} \\
  \dot{X}_{fb} &= 0
\end{align}

\begin{align}                                                                          
  \dot{Y}_{nb} &= 0 \\                                         
  \dot{Y}_{nm} &= L_{s}*\cos(\Theta_{nb})*\dot{\Theta}_{nb} \\
  \dot{Y}_{t}  &= ?? \\
  \dot{Y}_{fm} &= L_{s}*\cos(\Theta_{fb})*\dot{\Theta}_{fb} \\
  \dot{Y}_{fb} &= 0 \\
\end{align}

>>>>

We want to find cartesian coordinates in terms of $L_n$ and $L_f$.\\

@@

@@

\begin{align}
  X_{t} &= L_n\cos(\Theta_{1}) \\
       &= \frac{L^2+L_n^2-L_f^2}{2L} \\
\end{align}

@@

\begin{align}
  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
  Y_{t} &= L_n\sin(\Theta_{1}) \\
  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
\end{align}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{nb} &= 0 \\
  X_{nm} &=  \\
  X_{t}  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
  X_{fm} &=  \\
  X_{fb} &= L \\
\end{align}

\begin{align}
  Y_{nb} &= 0 \\
  Y_{nm} &=  \\
  Y_{t}  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
  Y_{fm} &=  \\
  Y_{fb} &= 0
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= \\
  \dot{X}_{t } &= \frac{L^2+2L_n\dot{L}_n-2L_f\dot{L}_f}{2L} \\
  \dot{X}_{fm} &= \\
  \dot{X}_{fb} &= 0
\end{align}

\begin{align}                                                                          
  \dot{Y}_{nb} &= 0 \\                                         
  \dot{Y}_{nm} &= \\
  \dot{Y}_{t}  &= \frac{L_n}{2\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2}} * \big(\frac{(-L^2L_n^{-2}+\dot{L}_n - 2L_f\dot{L}_nL_n^{-1} + L_f^2L_n^{-2}}{2L}\big) - think this is rite?\\
  \dot{Y}_{fm} &= \\
  \dot{Y}_{fb} &= 0 \\
\end{align}
